\documentclass{article}
\usepackage[utf8,applemac]{inputenc}
\usepackage{etaremune}
\usepackage{enumitem}
\usepackage{times}
\usepackage[numbers]{natbib}
\usepackage{xcolor,color}
\usepackage[hyphens]{url}
\urlstyle{same}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[colorlinks=true,linkcolor=myblue,citecolor=myblue,urlcolor=myblue]{hyperref}
\definecolor{myblue}{RGB}{0,0,170} 
\usepackage{geometry}
 \geometry{
 total={170mm,225mm},
 left=20mm,
 top=25mm,
}

%% bibliography with multiple entries
\usepackage[resetlabels,labeled]{multibib}
\newcites{thes,jrnl,conf,tech,invt,pres}{{ },{ },{ },{ },{ },{ }}

%% reverse numbering of bibliography
\usepackage{etaremune,etoolbox}
\makeatletter
\AtBeginDocument{
  \renewenvironment{thebibliography}[1]
  {
    \begin{etaremune}[itemsep=0mm]
      \let\citeN\cite\let\shortcite\cite\let\citeasnoun\cite}
    {\bibitem@fin\bibpostamble
      \def\@noitemerr{\PackageWarning{natbib}{Empty `thebibliography' environment}}%
    \end{etaremune}}
}
\patchcmd{\@lbibitem}{\item[\hfil\NAT@anchor{#2}{\NAT@num}]}{\item}{}{}
\makeatother

\begin{document}
\begin{center}
  {\bf\LARGE Sungho Shin}
\end{center}
\begin{center}
  {Mathematics and Computer Science Division}, {Argonne National Laboratory}\\
  Email: \href{mailto:sshin@anl.gov}{sshin@anl.gov} $|$ Web: \href{https://sunghoshin.com}{sunghoshin.com} $|$ Twitter: \href{https://twitter.com/SunghoShinSS}{@SunghoShinSS} $|$ Github: \href{https://github.com/sshin23}{@sshin23}
\end{center}

\section*{Education}
\begin{itemize}[leftmargin=*]
\item[]{\bf Ph.D. in Chemical Engineering} (2016 -- 2021)\\
  {\bf University of Wisconsin-Madison}, Madison, Wisconsin, USA. \\
  Minor: Industrial Engineering\\
  Thesis Advisor: Victor M. Zavala\\
  Thesis Title: Graph-Structured Nonlinear Programming: Properties and Algorithms
\item[]{\bf B.S. in Chemical Engineering} and {\bf Mathematics} (2010 -- 2016$^*$)\\
  {\bf Seoul National University}, Seoul, South Korea.\\
  Thesis Advisors: Jong Min Lee (Chemical Engineering) and Seng Yeal Ha (Mathematics)\\
  $^*$Military service in Republic of Korea Army (2012 -- 2014).
\end{itemize}

\section*{Research Interests}
\begin{itemize}[leftmargin=*]
\item[] control theory; sequential decision making; model predictive control; nonlinear optimization; numerical optimization; distributed optimization; decomposition algorithms; energy systems
\end{itemize}

\section*{Professional Appointments}
\begin{itemize}[leftmargin=*]
\item[] {\bf Postdoctoral Appointee} (2021 -- Present)\\
  Mathematics and Computer Science Division, Argonne National Laboratory. \\
  Supervisor: Mihai Anitescu.
\item[] {\bf Research Assistant} (2016 -- 2021)\\
  Department of Chemical and Biological Engineering, University of Wisconsin-Madison. \\
  Supervisor: Victor M. Zavala.
\item[] {\bf Research Intern} (2020)\\
  Advanced Network Science Initiative, Los Alamos National Laboratory. \\
  Supervisor: Carleton Coffrin and Kaarthik Sundar.
\item[] {\bf Research Intern} (2018)\\
  Mathematics and Computer Science Division, Argonne National Laboratory. \\
  Supervisor: Mihai Anitescu.
\item[] {\bf Research Intern} (2016)\\
  Energy Process Engineering Laboratory, Seoul National University. \\
  Supervisor: Jong Min Lee.
\end{itemize}

\section*{Publications}
\subsection*{Thesis}
\renewcommand*{\labelenumi}{[T\theenumi]}
\nocitethes{*}
\bibliographystylethes{custom}
\bibliographythes{thes}
\subsection*{Journal Publications}
\renewcommand*{\labelenumi}{[J\theenumi]}
\nocitejrnl{*}
\bibliographystylejrnl{custom}
\bibliographyjrnl{jrnl}
\subsection*{Conference Publications}
\renewcommand*{\labelenumi}{[C\theenumi]}
\nociteconf{*}
\bibliographystyleconf{custom}
\bibliographyconf{conf}
\subsection*{Book Chapters, Technical Reports, and Others}
\renewcommand*{\labelenumi}{[B\theenumi]}
\nocitetech{*}
\bibliographystyletech{custom}
\bibliographytech{tech}

\section*{Honors and Awards}
\begin{itemize}[leftmargin=*]
\item[] {\bf IFAC NMPC Young Author Award} (2021).
\item[] {\bf IFAC ADCHEM Young Author Award} (2021).
\item[] {\bf AIChE CAST Directors' Student Presentation Award} (2020).
\item[] {\bf Grainger Wisconsin Distinguished Graduate Fellowship} (2020 -- 2021).
\item[] {\bf Travel Awards} (CDC 2020; Wisconsin Student Research Grants Competition 2019; MLSE 2019)
\item[] {\bf Kwanjeong Scholarship} (2016 -- 2020).
\item[] {\bf Korea Presidential Science Scholarship} (2010 -- 2016).
\end{itemize}

\section*{Presentations}
\subsection*{Invited Talks}
\renewcommand*{\labelenumi}{[I\theenumi]}
\nociteinvt{*}
\bibliographystyleinvt{custom}
\bibliographyinvt{invt}
\subsection*{Conference Talks}
\renewcommand*{\labelenumi}{[P\theenumi]}
\nocitepres{*}
\bibliographystylepres{custom}
\bibliographypres{pres}

\section*{Software Products}
\begin{enumerate}
\renewcommand*{\labelenumi}{[S\theenumi]}
\item {\bf MadNLP.jl} (Main developer): a solver for nonlinear programming.\\
  \url{https://github.com/MadNLP/MadNLP.jl}
\item {\bf MadDiff.jl} (Main developer): an automatic differentiation and algebraic modeling tool.\\
  \url{https://github.com/sshin23/MadDiff.jl}
\item {\bf BlockNLPModels.jl} (Contributor): a data structure for block nonlinear programming models.\\
  \url{https://github.com/exanauts/BlockNLPModels.jl}
\item {\bf BlockNLPAlgorithms.jl} (Contributor): a decomposition solver for block BlockNLPModels.\\
  \url{https://github.com/exanauts/BlockNLPAlgorithms.jl}
\item {\bf Plasmo.jl} (Contributor): a graph-based algebraic modeling framework.\\
\url{https://github.com/plasmo-dev/Plasmo.jl}
\item {\bf SBML2Julia} (Contributor): a tool to for estimating parameters of models in SBML format.\\
\url{https://github.com/paulflang/SBML2Julia}
\end{enumerate}

\section*{Teaching Experience}
\begin{itemize}[leftmargin=*]
\item[] {\bf Teaching Assistant}, Statistics for Chemical Engineers, UW-Madison (Spring 2019)
\item[] {\bf Teaching Assistant}, Process Dynamics and Control, UW-Madison (Fall 2018, Fall 2017)
\item[] {\bf Tutor}, Process Control and Design, Seoul National University (Fall 2015)
\item[] {\bf Tutor}, Process Fluid Mechanics, Seoul National University (Spring 2015)
\item[] {\bf Tutor}, Basic Chemistry, Seoul National University (Spring 2015)
\end{itemize}

\section*{Mentoring Experience}
\begin{itemize}[leftmargin=*]
\item[] Undergraduate: Sang-il Kwon (UW-Madison, Fall 2017)
\item[] Graduate Interns: Rishabh Gupta (University of Minnesota, Spring 2022); David Cole (UW-Madison, Summer 2022).
\end{itemize}

\section*{Professional Services}
\subsection*{Academic Services}
\begin{itemize}[leftmargin=*]
  \item[] Co-Chair and Reviewer, AIChE Annual Meeting CAST Division (10B co-chair/reviewer; 10E reviewer; 2022); Judge for Reserach Presentation Sessions, Argonne Postdoctoral Research and Career Symposium (2022).
\end{itemize}

\subsection*{Peer Review}
\begin{itemize}[leftmargin=*]
\item[] AIChE Journal; Automatica; Computers \& Chemical Engineering; IEEE Control Systems Letters; IEEE Transactions on Control Systems Technology; IEEE Transactions on Automatic Control; IFAC Conference on Nonlinear Model Predictive Control; IFAC International Symposium on Advanced Control of Chemical Processes; Industrial \& Engineering Chemistry Research; Journal of Optimization Theory and Applications; SIAM Journal on Optimization
\end{itemize}

\subsection*{Outreach}
\begin{itemize}[leftmargin=*]
\item[] SCIENCountErs (volunteered to help build a pipeline of STEM students from underrepresented groups; Fall 2018).
\end{itemize}

\section*{Skills}
\begin{itemize}[leftmargin=*]
\item[] Language: English and Korean
\item[] Programming: Julia; MATLAB; Python; C/C++; \LaTeX; git; MPI; linux; shell scripting
\end{itemize}

\section*{References}
\begin{itemize}[leftmargin=*]
\item[] Provided upon request.
\end{itemize}

{\noindent\it Last updated: \today}

\end{document}
