\documentclass{article}
\usepackage[utf8,applemac]{inputenc}
\usepackage{etaremune}
\usepackage{enumitem}
\usepackage{times}
\usepackage[numbers]{natbib}
\usepackage{xcolor,color}
\usepackage[hyphens]{url}
\urlstyle{same}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[colorlinks=true,linkcolor=myblue,citecolor=myblue,urlcolor=myblue]{hyperref}
\definecolor{myblue}{RGB}{0,0,170} 
\usepackage{geometry}
 \geometry{
 total={170mm,225mm},
 left=20mm,
 top=25mm,
}

%% bibliography with multiple entries
\usepackage[resetlabels,labeled]{multibib}
\newcites{thes,jrnl,conf,invt}{{ },{ },{ },{ }}

%% reverse numbering of bibliography
\usepackage{etaremune,etoolbox}
\makeatletter
\AtBeginDocument{
  \renewenvironment{thebibliography}[1]
  {
    \begin{etaremune}[itemsep=0mm]
      \let\citeN\cite\let\shortcite\cite\let\citeasnoun\cite}
    {\bibitem@fin\bibpostamble
      \def\@noitemerr{\PackageWarning{natbib}{Empty `thebibliography' environment}}%
    \end{etaremune}}
}
\patchcmd{\@lbibitem}{\item[\hfil\NAT@anchor{#2}{\NAT@num}]}{\item}{}{}
\makeatother

%% to shorten
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{4pt}{4pt}
\titlespacing*{\subsection}{0pt}{4pt}{4pt}

\begin{document}
\begin{center}
  {\bf\LARGE Sungho Shin}
\end{center}
\begin{center}
  {Postdoctoral Appointee (email: \href{mailto:sshin@anl.gov}{sshin@anl.gov})}\\
  {Mathematics and Computer Science Division},\\
  {Argonne National Laboratory}\\
\end{center}

\section*{Education}
\begin{itemize}[leftmargin=*,itemsep=0em]
\item[]{\bf Ph.D. in Chemical Engineering}, {\bf University of Wisconsin-Madison} (2021; Advisor: Victor M. Zavala)
\item[]{\bf B.S. in Mathematics} and {\bf Chemical Engineering}, {\bf Seoul National University} (2016).
\end{itemize}

\section*{Professional Appointments}
\begin{itemize}[leftmargin=*,itemsep=0em]
\item[] {\bf Postdoctoral Appointee} (June 2021 -- Present), Mathematics and Computer Science Division, Argonne National Laboratory. (Supervisor: Mihai Anitescu).
\item[] {\bf Research Assistant} (Sept. 2016 -- May 2021), Department of Chemical and Biological Engineering, University of Wisconsin-Madison. (Supervisor: Victor M. Zavala).
\item[] {\bf Research Intern} (June 2020 -- Sept. 2020), Advanced Network Science Initiative, Los Alamos National Laboratory. (Supervisor: Carleton Coffrin and Kaarthik Sundar).
\item[] {\bf Research Intern} (May 2018 -- Aug. 2018), Mathematics and Computer Science Division, Argonne National Laboratory. (Supervisor: Mihai Anitescu).
\item[] {\bf Research Intern} (Jan. 2016 -- June 2016), Energy Process Engineering Laboratory, Seoul National University. (Supervisor: Jong Min Lee).
\end{itemize}

\section*{Honors and Awards}
\begin{itemize}[leftmargin=*,itemsep=0em]
\item[] {\bf IFAC NMPC Young Author Award} (July 2021).
\item[] {\bf IFAC ADCHEM Young Author Award} (June 2021).
\item[] {\bf AIChE CAST Directors' Student Presentation Award} (Nov. 2020).
\item[] {\bf Grainger Wisconsin Distinguished Graduate Fellowship} (Sept. 2020 -- June 2021).
\item[] {\bf Kwanjeong Scholarship} (Sept. 2016 -- Aug. 2020).
\item[] {\bf Korea Presidential Science Scholarship} (Mar. 2010 -- Feb. 2016).
\end{itemize}

\section*{Publications}
\subsection*{Thesis}
\renewcommand*{\labelenumi}{[T\theenumi]}
\nocitethes{*}
\bibliographystylethes{custom}
\bibliographythes{thes}
\subsection*{Journal Publications}
\renewcommand*{\labelenumi}{[J\theenumi]}
\nocitejrnl{*}
\bibliographystylejrnl{custom}
\bibliographyjrnl{jrnl}
\subsection*{Conference Publications}
\renewcommand*{\labelenumi}{[C\theenumi]}
\nociteconf{*}
\bibliographystyleconf{custom}
\bibliographyconf{conf}

\section*{Invited Talks}
\renewcommand*{\labelenumi}{[I\theenumi]}
\nociteinvt{*}
\bibliographystyleinvt{custom}
\bibliographyinvt{invt}


\end{document}
